Karpov, Kasprov, Anand

### 2022-05-30 inst/kka.Rmd
chess3

```{r,maxewhitedrawlike,cache=TRUE}
f <- function(v){
    lambda <- v[1]
    D      <- v[2]
    H <- white_draw3(kka_array, lambda,D)
    max(maxp(H,justlikes=TRUE))
}	
f(c(1.5,2.3))
```

@@

@@

```{r,label=savecurlingdataset,cache=TRUE}
save(kka,karpov_kasparov_anand,kka_3draws,kka_3whites,kka_array,file="kka.rda")
```

>>>>

```{r,maxewhitedrawlike,cache=TRUE}
f <- function(v){
    lambda <- v[1]
    D      <- v[2]
    H <- white_draw3(kka_array, lambda,D)
    max(maxp(H,n=1,justlikes=TRUE))
}	
f(c(1.5,2.3))
```

@@

Optimize:

```{r,label=useoptimopencloseforf,cache=TRUE}
(o <- optim(par=c(2.1,2.4),fn=f,control=list(fnscale = -1)))
```

```{r,createchess3}
(chess3 <- f(o$par))
```

@@

```{r,label=savecurlingdataset,cache=TRUE}
save(kka,karpov_kasparov_anand,kka_3draws,kka_3whites,kka_array,chess3,file="kka.rda")
```
